---
title: "README"
author: "Charles McCann, Dominique Edwards, Hari Narayan Sanadhya, Huynh vu"
date: "March 20, 2017"
output: 
  md_document:
    variant: markdown_github
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# GDP ranking - examine GDP with respect to Income Group 
## Project Purpose
Using the World Bank datasets, download and examine the effect of income group of a country on its GDP value. This includes downloading and cleansing of the data and then perform the analysis.

## Project Folder and File structure
* Folders: - 
  1. source: - This folder contains the R source code used for tidying the raw datasets.
  2. graphs: - This folder contains all the graphs that are generated during this study.
  3. data: - This folder contains raw data files, the tidied files and merged file.
* Files: -
  1. data/edu.csv: - This is the raw educational statistics file from World Bank containing some of the internationally comparable indicators that describes education access, progression, completion, literacy, teachers, population, and expenditures. The indicator that we will be using in this study is the Income Group.
  2. data/gdp.csv: - This is the raw GDP file from World Bank which contains GDP data of 190 different countries in the world.
  3.data/cleaned_EDU_Data.txt: - This is the tidy version of education statistics file (edu.csv) generated by the execution of the R code 'EDU_data.R'.
  4. data/cleaned_GDP_Data.txt: - This is the tidy version of GDP data file (gdp.csv) generated by the execution of the R code 'GDP_data.R'.
  5. data/merged_Data.txt: - This file contains the merged data of the two files cleaned_EDU_Data and cleaned_GDP_Data, merged by Country Code.
  6. graphs/CountryCode_vs_GDP.png: - This is the plot of the GDP for all the countries. Countries with different income group have different colors.
  7. graphs/Modified CountryCode_vs_GDP.png: - This is the plot splitted vertically to represent the GDP of countries with same income group in each splitted section.
  8. source/EDU_data.R: - R code that performs the tidying of the raw education statistics file (edu.csv).
  9. source/GDP_data.R: - R code that performs the tidying of the raw GDP data file (gdp.csv).
  10. README.md: - This file includes an explanation of the purpose of the project and the other files.
  11. README.Rmd: - The R markdown file that creates the README.md file.
  12. report.md: - This markdown file provides the details of the analysis performed on the cleaned data files including the introduction, analysis code, output of the code and conclusion derived from the analysis.
  13. report.Rmd: - The R markdown file that creates the report.md file.
  14. Makefile: - It lists all the steps to regenerate this study aimed to find relationship between the income group of a country with its GDP value.
  15. GDP.Rproj: - This is the R project file for this project.
  16. .gitignore: - This file specifies intentionally untracked files that Git should ignore. 
  
  
# Session Information
```{r echo=FALSE}
sessionInfo()
```
