---
title: "Case Study 1"
fontsize: 10pt
output: html_document

---
```{r echo=FALSE}
merged_Data <- read.csv("data/merged_Data.csv",header=T, sep = "|")
```
<b>Introduction</b>
<br>
<p>
...
</p>
<br>
<br>

<b>Question 1: How many IDs matched?</b>
```{r}
# The following R code calculates the # of rows after successfully merging the GDP and Education datasets.
nrow(merged_Data)
```
<br>

<b>Question 2: Sort the data frame in ascending order by GDP (so United States is last). What is the 13th country in the resulting data frame?</b>
```{r}
# The following R code displays the first 13 countries of the merged and then sorted by GDP data.
sort_by_GDP <- merged_Data[order(merged_Data$GDP.in.Millions.USD),]
head(sort_by_GDP$Country, 13)
```
<br>

<b>Question 3: What are the average GDP rankings for the "High income: OECD" and "High income: nonOECD" groups</b>
```{r}
# get average of all high income: OECD


# get average of all high income: nonOECD

```
<br>

<b>Question 4: Plot the GDP for all of the countries. Use ggplot2 to color your plot by Income Group.</b>
```{r}
# plot GDP

```
<br>

<b>Question 5: Cut the GDP ranking into 5 separate quantile groups. Make a table versus Income.Group. How many countries are Lower middle income but among the 38 nations with highest GDP?</b>
```{r}
# ?????
```
<br>

<b>Conclusion</b>
<br>
<p>
...
</p>
